Discovery of the first quadruple gravitationally lensed quasar candidate with Pan-STARRS

### 2017-05-15 paper4.tex
finished updating the draft

In this letter we report the serendipitous discovery of a quadruply imaged gravitationally lensed quasar (quad lens) candidate from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS1, hereafter PS1) released images. To our knowledge, if proven with spectroscopic observations, this would be the first gravitational lens discovered in the PS1 data. There are only about two dozens known quad lenses on the whole sky \citep{masterlens}, and therefore increasing this sample is of high priority. We model the system to provide evidence in support of its lensing nature, and we conclude with the necessity of obtaining spectroscopic confirmation. Due to its position, this is not possible until the end of the year.

@@

NEED A PARAGRAPH ON THE OTHER QUADS OBSERVED SO FAR AND THEIR IMPORTANCE, AND REWRITE THIS PARAGRAPH. The importance of such quasars is illustrated by the wealth of science this lens has provided over the years.  Due to magnification, \citet{reis14} were able to measure the black hole spin in this quasar based on reflection features in X-ray spectra, which has important implications for studies of galaxy evolution. High resolution Hubbble images allowed \citet{bre08} to use source reconstruction to resolve the quasar host galaxy and reveal its structure. We hope this new lens will provide a similarly important results in the near future and in this letter we present results based solely on the PS1 data.

We assume a cosmological model with $\Omega_M = 0.274$, $\Omega_L = 0.726$, and h = 0.71. All magnitudes are in the AB system. The structure of the paper is as follows:
In Section 2 we infer relative astrometry, photometry and photometric redshifts. In Section 3 we fit a mass model to the system. Discussions, conclusions and future works are presented in Section 4.

\section{MORPHOLOGICAL MODELING}

We used the stacked images from PS1 in all five filters in order to perform a morphological modeling. We present a close-up color image of the system in Fig.~\ref{lens}, which clearly shows four objects within $\lesssim 3.8\arcsec$ of each other. The three brightest of these are arranged in an arc-like configuration. We originally used a point spread function (PSF) constructed from stars in the PS1 field of view (FOV), but this left large residuals at the locations of the four objects, significant enough to affect the derived parameters. We suspected that this is due to spatial variation in the PSF across the PS1 FOV, and therefore adopted a technique of fitting the system with an analytical PSF, assumed to not change on the small scale represented by the system. We did this using Hostlens \citep{rus16}, a variant of ``glafic'' \citep{ogu10} which uses $\chi^2$ minimization in order to fit point sources as well as S{\'e}rsic \citep{ser63} profiles convolved with an analytical PSF. The analytical PSF is comprised of two concentric Moffat \citep{mof69} profiles, each one with its own full-width half maximum, ellipticity, orientation, and shape parameter. The two profiles are also characterized by a relative flux of one to the other. We successfully modeled the four objects as point sources convolved with the PSF, therefore showing that they are point-like. Our strategy was to run Hostlens starting from 100 different positions in the parameter space, select the best of the resulting models, and further run 10 Markov Chain Monte Carlo (MCMC) chains using the Metropolis–Hastings algorithm around it. The chains consist of one million steps, with an acceptance rate of $\sim0.3$, and we removed the first 1/5 of these (the ``burn-in'' steps). We also checked that the chains have converged, using the method of \citet{gel95}. We show MCMC-derived uncertainties between the various analytical parameters in Fig.~\ref{mcmc_hostlens}. In order to quantify additional uncertainties inherent in our method due to the non-analytical nature of the ``true'' PSF, we ran 100 simulations where we add noise of similar properties to the real images, on top of the best-fit model. Here, we created the best-fit model by using a PSF constructed from nearby stars, and we ran Hostlens on each of the 100 simulations, using an analytical PSF. As a final estimate of our uncertainties, we used the maximum between the MCMC-derived uncertainties and those from the simulations. We were able to obtain much improved residuals in all bands, and we show these in Fig.~\ref{hostlens}.

We found conspicuous residual in the $i$, $z$ and $y$ bands, just north of the faint point source (Fig.~\ref{hostlens}, middle row). This is consistent with the discovery of a lensing galaxy, in support of the lensing nature of this system. Due to the relatively low signal to noise ratio and the proximity of the point sources, we were unable to fit the morphology of this galaxy with free parameters. The red colors, suggested by the non-detection in the bluer bands, suggest that it is a red, early-type galaxy. As a result, we modeled it with a S{\'e}rsic index of 4, typical of early-type galaxies. We checked that this produces a better fit than a S{\'e}rsic index of 1. For the S{\'e}rsic profile we used an axis ratio of 1 and we fixed the effective radius at $0.5\arcsec$. As the galaxy is most conspicuous in the $i$ and $y$ bands, we consider the most reliable estimate of the relative positions of all objects to be derived from the weighted average of the positions measured in these two bands, where we weight by the inverse of the measured uncertainties. The resulting astrometry, as well as photometry in each band, are shown in Table~1. We have orrected the magnitudes for galactic extinction using the maps of \citet{sch11}.

@@

chi from how many bands

{\bf This has to be changed to use Le Phare method }
To calculate photometric redshift we used the method of \citet{wu10}, which is based on Sloan Digital Sky survey (SDSS) colors. PS1 bands are similar but not identical to the SDSS bands and we used the corrections of \citep{fin16} to obtain magnitudes in the SDSS system. Folowing \citet{wu10} we minimize ${\chi}^2$ to obtain redshits for each of the sources. We plot $\chi^2_{\nu}$ in Figure~\ref{redshift} for each quasar image and also fitting all togehter. In the latter case we obtain the best fit at z $=$ 0.820$^{+0.006}_{-0.007}$.

The photometric, astrometric and redshift results are summarized in Table~1.

Due to blending of A, B and C components, both Gaia \citep{gaia} and PS1 catalogs identified sources A and D only. 
PS1 psf magnitudes for A are in general smaller than what we obtained probably due to blending, but for D they are very similar to our uncorrected magnitudes: 18.599$\pm$0.013,  18.153$\pm$0.002,  18.079$\pm$0.007,  17.843$\pm$0.0093,  17.534$\pm$0.023. Gaia G magnitudes are 15.17 and 18.13 for A and D, respectively.
We will use the Gaia position for component D as absolute astrometric reference position for our lens: 26.7923069811, 46.5112731937. The errors for this position are 15.6 and 8.9 mas, respectively.

The lens is also bright in infrared, the unresolved WISE magnitudes for the lens are: 11.524$\pm$0.022, 10.434$\pm$0.020, 6.769$\pm$0.015 ,4.518$\pm$0.023  in the WISE bands $-$ W1, W2, W3 and W4, respectively. The WISE colors W1$-$W2$=$1.1 and W2$-$W3$=$3.7 match very well those of quasars at relatively low redshift \citep[e.g.][]{wu12}.

Finally, the lens is very likely a radio source. The NRAO VLA Sky Survey (NVSS) images show a source at the lens position, 2MASX J01471020+4630433 has a flux of 12.6 mJy at 1.4 GHz. The listed position for this source is only 3 arcsec away from the center of the lens. We are in the process of observing the lens with the Very Large Baseline Array (VLBA).

@@

We used the gravlens software to model the gravitational lens \citep{kee01} using the averaged positions from the i and i bands, where the lensing galaxy is better detected. We chose not to use the fluxes in the modeling because it is very well known that they usually show large discrepancies from the models due to microlensing, millilensing or extinction. A good example is RX J1131-1231 which was mentioned in the introduction \citep{slu08}. Moreveover, fitting the fluxes could affect the results of models which do not account for small-scale structure or dust.  We therefore only used the observed fluxes to compare with the model predictions after the modeling was performed.

We use a Singular Isothermal Ellipsoid (SIE) with shear. The parameters for the best fit models are: $b = 1.932_{-0.011}^{+0.008}$, $x_0 = 0.284\pm0.006$, $y_0 = -2.301_{-0.049}^{0.052}$, $e_c = 0.163_{-0.070}^{+0.063}$, $e_s = -0.035_{-0.024}^{+0.023}$, $\gamma_c = 0.122_{-0.016}^{+0.015}$, $\gamma_s = 0.065\pm0.005$. The predicted positions and magnitudes are presented in Table~1. In Figure~\ref{model} we show the critical curve and the caustics. The $\chi^2_{\nu}$ is 0.8, with most dicrepancy coming from the position of the galaxy. We explored the range of models using MCMC methods. The predicted magnitude differences are shown in Table1~1 and a comparison with the observed values are shown in Figure~\ref{modelphot}. As expected we indeed find large discrepancies.

 The model suggest that the two outer images should be similar in brightness.  This is interesting because there are some physical effects that can cause observed image brightnesses to differ from the predictions of simple lens models. Firstly light can be affected as it propagates through the main lens galaxy, for example by differential extinction.  This possibility is interesting in light of the color differences between images.  Propagation effects tend to be more important at optical wavelengths than at radio wavelengths; this is particularly true of extinction, although there can be scatter broadening at radio wavelengths. Secondly, the light can be affected by stars in the lens galaxy through microlensing.  This mainly affects optical wavelengths. Finally, the light can be affected by dark matter substructure in the lens galaxy through millilensing.  This could affect all wavelengths.

Measuring the flux ratios in radio with VLBA would provide valuable information that will help us test the lensing hypothesis and understand the various physical effects at play and better constrain the models

@@

\begin{itemize}
\item The presence of four point-like images within $\lesssim 3.8\arcsec$ of each other, with similar colors, completely consistent with quasars templates, but less consistent with stars and galaxies.
\item The detection of a red galaxy between the point source, such that the relative positions of all five objects are fully consistent with a well-known ``cusp'' configuration. We successfully reproduce this configuration using a SIE + shear model for the lensing galaxy. Further more, the brightness ranking of the point-like images is consistent with the ones predicted by the model.
 \item The photometric redshift analysis shows that the galaxy is of elliptical template, typical for lensing galaxies, and of redshift smaller than the point sources. For the inferred redshifts, the velocity dispersion and mass of the lensing galaxy are consistent with those of typical galaxies.
\end{itemize}

@@

\bibitem[Bertin \& Arnouts(1996)]{ber96} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
\bibitem[Brewer \& Lewis(2008)]{bre08} Brewer, B.~J., \& Lewis, G.~F.\ 2008, \mnras, 390, 39

\bibitem[Chambers et al.(2016)]{cha16} Chambers, K.~C., Magnier, E.~A., Metcalfe, N., et al.\ 2016, arXiv:1612.05560 
\bibitem[Finkbeiner et al.(2016)]{fin16} Finkbeiner, D.~P., Schlafly, E.~F., Schlegel, D.~J., et al.\ 2016, \apj, 822, 66
\bibitem[Gaia Collaboration et al.(2016)]{gaia} Gaia Collaboration, Brown, A.~G.~A., Vallenari, A., et al.\ 2016, \aap, 595, A2 
\bibitem[Gelman(1995)]{gel95} Gelman A. et al., 1995, Bayesian Data Analysis. CRC Press, Boca Raton, FL
\bibitem[Keeton(2001)]{kee01} Keeton, C.~R.\ 2001, arXiv:astro-ph/0102340

\bibitem[Moffat (1969)]{mof69} Moffat, A. F. J.\ 1969, \aap, 3, 455

%% \bibitem[Mateos et al.(2012)]{mat12} Mateos, S., Alonso-Herrero, A., Carrera, F.~J., et al.\ 2012, \mnras, 426, 3271 
\bibitem[Oguri \& Marshall(2010)]{ogu10} Oguri, M., \& Marshall, P.~J.\ 2010, \mnras, 405, 2579 
\bibitem[Oguri (2010)]{ogu10} Oguri M., 2010, PASJ, 62, 1017

@@

\bibitem[Peng et al.(2010)]{peng10} Peng, C.~Y., Ho, L.~C., Impey, C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097 
\bibitem[Reis et al.(2014)]{reis14} Reis, R.~C., Reynolds, M.~T., Miller, J.~M., \& Walton, D.~J.\ 2014, \nat, 507, 207 
\bibitem[Rusu et al.(2016)]{rus16} Rusu C.~E., et al., 2016, MNRAS, 458, 2

\bibitem[Schlafly \& Finkbeiner(2011)]{sch11} Schlafly, E.~F., \& Finkbeiner, D.~P.\ 2011, \apj, 737, 103 
\bibitem[S{\'e}rsic (1963)]{ser63} S{\'e}rsic J.~L., 1963, BAAA, 6, 41 
\bibitem[Sluse et al.(2003)]{slu03} Sluse, D., Surdej, J., Claeskens, J.-F., et al.\ 2003, \aap, 406, L43 
\bibitem[Sluse et al.(2006)]{slu06} Sluse, D., Claeskens, J.-F., Altieri, B., et al.\ 2006, \aap, 449, 539 
\bibitem[Sluse et al.(2008)]{slu08} Sluse, D., Eigenbrod, A., Courbin, F., et al.\ 2008, Manchester Microlensing Conference, 20

@@

\bibitem[Wu \& Jia(2010)]{wu10} Wu, X.-B., \& Jia, Z.\ 2010, \mnras, 406, 1583

\bibitem[Wu et al.(2012)]{wu12} Wu, X.-B., Hao, G., Jia, Z., Zhang, Y., \& Peng, N.\ 2012, \aj, 144, 49 
\bibitem[York et al.(2000)]{york00} York, D.~G., Adelman, J., Anderson, J.~E., Jr., et al.\ 2000, \aj, 120, 1579

@@

\begin{figure}
\epsscale{1}
\plotone{hostlens.eps}
\caption{
Original images ($10\arcsec\times10\arcsec$, first row) and residuals after subtracting the best-fit model with Hostlens. From left to right: $g$, $r$, $i$, $z$, $y$-band. In the second raw, the lensing galaxy is not including in the modeling, whereas in the third raw it is. The images are in linear scale, and cover the full dynamic range.}
\label{hostlens}
\end{figure}

\begin{figure}
\epsscale{0.6}
\plotone{critcrv1.eps}
\caption{
Gravitational lens modelling. The blue and red lines show the critical curves and caustics, respectively. The green dot shows the quasar position in the source plane, and the black dots show the lens and the observed image positions.}
\label{model}
\end{figure}

>>>>

Since the serendipitous discovery of the first gravitationally lensed quasar \citep{wal79}, these systems have become powerful probes of astrophysics and cosmology, as illustrated by the wealth of science they have provided over the years. For example, \citep[e.g.,][]{pen06,din17} have studied the coevolution of supermassive black holes and the quasar hosts harboring them up to high redshift. \citet{ogu12,bon17} and others have constrained the cosmological constant and the Hubble constant from samples of lensed quasars. Flux ratio anomalies have revealed luminous satellites or set constraints on dark matter substructure in the lensing galaxies \citep[e.g.,][]{chi05,mck07,fad12}. Ensembles of lenses have revealed the structure of massive galaxies \citep[e.g.,][]{kho00,ogu14}. Other insights have been gained into the quasar accretion disks \citep[e.g.,][]{dai10}, the broad-line regions \citep[e.g.,][]{slu12}, and the black hole spin \citep{reis14}.

These applications all require increasingly large samples of lensed quasars, and in particular quadruply lensed quasars (quads), due to the increased number of modeling constraints they provide. To date, there are only about two dozen known quads over the whole sky. Due to the rare nature of lensed quasars, large scale surveys of sufficient depth and resolution are required to significantly increase the present sample \citep{ogu10}. As such surveys have become available, pioneering searches for lensed quasars, such as the Cosmic Lens All Sky Survey \citep[CLASS;][]{mye03} have been succeeded by the SDSS Quasar Lens Search \citep[SQLS;][]{ogu06}, and more recently by the STRong lensing Insight in the Dark Energy Survey \citep[STRIDES;][]{agn15} and the Survey of Gravitationally-lensed Objects in HSC Imaging \citep[SuGOHI;][]{son17}, amongst others.

In this letter we report the serendipitous discovery of a quad lensed quasar candidate from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS1, hereafter PS1) released images. To our knowledge, if proven with spectroscopic observations, this would be the first gravitational lens discovered in the PS1 data. We model the system to provide evidence in support of its lensing nature, and we conclude with the necessity of obtaining spectroscopic confirmation. Due to its position, this is not possible until the end of the year.

@@

The structure of the paper is as follows:
In Section 2 we infer relative astrometry, photometry and photometric redshifts. In Section 3 we fit a mass model to the system. Discussions, conclusions and future works are presented in Section 4. We assume a cosmological model with $\Omega_M = 0.274$, $\Omega_L = 0.726$, and $h$ = 0.71. All magnitudes are in the AB system.

\section{ASTROMETRY AND PHOTOMETRY}

We used the stacked images from PS1 in all five filters in order to perform a morphological modeling. We present a close-up color image of the system in Fig.~\ref{lens}, which clearly shows four objects within $\lesssim 3.8\arcsec$ of each other. The three brightest of these (A, B and C) are arranged in an arc-like configuration. The PS1 catalogues identify only the sources A and D, with B and C being blended with A.

We originally used a point spread function (PSF) constructed from stars in the PS1 field of view (FOV), but this left large residuals at the locations of the four objects, significant enough to affect the derived parameters. We suspected that this is due to spatial variation in the PSF across the PS1 FOV, and therefore adopted a technique of fitting the system with an analytical PSF, assumed to not change on the small scale represented by the system. We did this using Hostlens \citep{rus16}, a variant of glafic \citep{ogu10b} which uses $\chi^2$ minimization in order to fit point sources as well as S{\'e}rsic \citep{ser63} profiles convolved with an analytical PSF. The analytical PSF is comprised of two concentric Moffat \citep{mof69} profiles, each one with its own full-width half maximum, ellipticity, orientation, and shape parameter. The two profiles are also characterized by a relative flux of one to the other. We successfully modeled the four objects as point sources convolved with the PSF, therefore showing that they are point-like. Our strategy was to run Hostlens starting from 100 different positions in the parameter space, select the best of the resulting models, and further run 10 Markov Chain Monte Carlo (MCMC) chains using the Metropolis–Hastings algorithm around it. The chains consist of one million steps, with an acceptance rate of $\sim0.3$, and we removed the first 1/5 of these (the ``burn-in'' steps). We also checked that the chains have converged, using the method of \citet{gel95}. We show MCMC-derived uncertainties between the various analytical parameters in Fig.~\ref{mcmc_hostlens}. In order to quantify additional uncertainties inherent in our method due to the non-analytical nature of the ``true'' PSF, we ran 100 simulations where we add noise of similar properties to the real images, on top of the best-fit model. Here, we created the best-fit model by using a PSF constructed from nearby stars, and we ran Hostlens on each of the 100 simulations, using an analytical PSF. As a final estimate of our uncertainties, we used the maximum between the MCMC-derived uncertainties and those from the simulations. We were able to obtain much improved residuals in all bands, and we show these in Fig.~\ref{hostlens}.

We found conspicuous residual in the $i$, $z$ and $y$ bands, just north of the faint point source (Fig.~\ref{hostlens}, middle row). This is consistent with the discovery of a lensing galaxy, in support of the lensing nature of this system. Due to the relatively low signal to noise ratio and the proximity of the point sources, we were unable to fit the morphology of this galaxy with free parameters. The red colors, suggested by the non-detection in the bluer bands, suggest that it is a red, early-type galaxy. As a result, we modeled it with a S{\'e}rsic index of 4, typical of early-type galaxies. We checked that this produces a better fit than a S{\'e}rsic index of 1. For the S{\'e}rsic profile we used an axis ratio of 1 and we fixed the effective radius at $0.5\arcsec$. As the galaxy is most conspicuous in the $i$ and $y$ bands, we consider the most reliable estimate of the relative positions of all objects to be derived from the weighted average of the positions measured in these two bands, where we weight by the inverse of the measured uncertainties. The resulting astrometry, as well as photometry in each band, are shown in Table~1. We have corrected the magnitudes for galactic extinction using the maps of \citet{sch11}.

In addition to the PS1 data, we have also looked for archival data of this system. The system is detected in the Gaia \citep{gaia} catalogues where, similar the the PS1 catalogues, only A and D are deblended by the automatic pipeline. We use the Gaia position for component D as absolute astrometric reference position for this system: 26.792307, 46.511273. The errors for these coordinates are 15.6 and 8.9 mas, respectively [NEEDS REFERENCE].

%PS1 psf magnitudes for A are in general smaller than what we obtained probably due to blending, but for D they are very similar to our uncorrected magnitudes: 18.599$\pm$0.013,  18.153$\pm$0.002,  18.079$\pm$0.007,  17.843$\pm$0.0093,  17.534$\pm$0.023. Gaia G magnitudes are 15.17 and 18.13 for A and D, respectively.

The system is also bright in the infrared, with the unresolved magnitudes being: 11.524$\pm$0.022, 10.434$\pm$0.020, 6.769$\pm$0.015, and 4.518$\pm$0.023  in the WISE bands $-$ W1, W2, W3 and W4, respectively. The WISE colors W1$-$W2$=$1.1 and W2$-$W3$=$3.7 match very well those of quasars at relatively low redshift \citep[e.g.][]{wu12}.

Finally, the system is very likely also a radio source. The NRAO VLA Sky Survey (NVSS) images show a source, 2MASX J01471020+4630433, with flux 12.6 mJy at 1.4 GHz. The listed position for this source is only 3 arcsec away from the center of the lens. We are currently in the process of further observing the system in the radio with the Very Large Baseline Array (VLBA). Radio data is useful for the study of lensed quasars, as it provides high-resolution imaging of the source, as well as fluxes not affected by microlensing and extinction.

@@

We aim to fit the photometry measured in Section 2 for the point-like sources and the faint red galaxy using spectral energy distribution (SED) templates. The colors of the point-like images are very similar (Table~1), consistent with being multiple images of the same source. Due to their point-like morphology, we suspect these to be quasars, and we therefore fit them with quasar templates in order to check the quality of the fit and to infer photometric redshifts. Photometric redshifts of quasars are notoriously difficult to constrain, due to the relatively featureless continua \citep{ric09} and the variable equivalent widths of the broad emission lines. We followed two approaches:
\begin{itemize}
\item We used the method of \citet{wu10}, which present quasar colors as a function of redshifts. This is based on Sloan Digital Sky survey (SDSS) colors. PS1 bands are similar but not identical to the SDSS bands and we used the corrections of \citep{fin16} to obtain magnitudes in the SDSS system. Following \citet{wu10}, we minimized ${\chi}^2$ to obtain redshifts for each of the point sources. We plot $\chi^2_{\nu}$ in Figure~\ref{redshift} for each quasar image, and also by fitting all sources together. We notice that the curves are quite consistent with each other, as expected from the similar colors of the sources. In the latter case we obtain the best fit at $z = 0.820^{+0.006}_{-0.007}$. We notice a second minimum at $z \sim2.6$. For both minima the $\chi^2_{\nu}$ is $\lesssim1$, indicative of a good fit. 
\item We fitted quasar templates using LePhare \citep{arn99,ilb06}. We obtained a best-fit redshift of $\sim 2.6-2.8$ for all four point sources, in agreement with the second peak of the method above. The $\chi^2$ is between 13 and 125 for 4 degrees of freedom (5 filters). We find poorer fits (larger $\chi^2$) if we use stellar or galactic SED templates, further supporting that the sources are quasars. In particular, the best-fit galaxy templates correspond to starburst galaxies at low redshift $\lesssim0.1$. At such low redshifts the sources would likely be resolved, not point-like. 
\end{itemize}

We also fitted a galaxy SED to the faint galaxy G, resulting in a best-fit $z = 0.57^{+0.20}_{-0.13}$, obtained for an early-type template. For this, we used the magnitudes measured in the $izy$ bands and assumed detection limits of 21 mag in the $gr$ bands, $\sim$ 2 mag fainter than the rest.

@@

The results of the previous sections show that the source is likely a quadruply imaged quasar, lensed by a foreground early-type galaxy. We subsequently modeled the observed configuration (the relative positions of the objects A,B,C,D and G) using gravlens \citep{kee01}. We chose not to use the observed relative fluxes as constraints, as it is well known that at these wavelengths they usually show large discrepancies due to microlensing, millilensing, intrinsic variability or extinction \citep[e.g.,][]{slu08}. For the mass profile of the lensing galaxy we use a Singular Isothermal Ellipsoid (SIE) with external shear. There are 8 constraints from the 4 image positions and 2 constraints from the galaxy position, for a total of 10. Also, there are 9 free parameters: 2 for the galaxy position, 1 for the Einstein radius, 2 for ellipticity, 2 for shear, and 2 for the source position. The model therefore has 1 degree of freedom.

For the best-fit mass model parameters, we find an Einstein radius $b = 1.932_{-0.011}^{+0.008}$, ellipticity $e_c = 0.163_{-0.070}^{+0.063}$, $e_s = -0.035_{-0.024}^{+0.023}$, and shear $\gamma_c = 0.122_{-0.016}^{+0.015}$, $\gamma_s = 0.065\pm0.005$. Here, we expressed the ellipticity and shear in quasi-cartesian coordinates, rather than polar coordinates, as the distribution of uncertainties is more gaussian. The two coordinate systems are related by $(e_c,\gamma_c) = (e,\gamma)\cos2(\theta_e,\theta_\gamma)$ and $(e_s,\gamma_s) = (e,\gamma)\sin2(\theta_e,\theta_\gamma)$. The uncertainties were determined using MCMC. The $\chi^2$ for this model is 0.8.

While the parameters derived above are independent of redshift, estimating the expected time delays between the images does require redshift information. Using the results of the previous Section, we have fixed the redshift of the source at 0.57. If we assume a source redshift of 0.82, we derive from the expression of the Einstein radius in a singular isothermal profile, $b=4\pi\left(\frac{\sigma}{c}\right)^2\frac{D_{ls}}{D_{s}}$, a velocity dispersion of $\sigma\sim500$ km/s. Here $c$ is the speed of light, and $D_{s},D_{ls}$ are the angular diameter distances to the source and between lens and source, respectively. This value is too large for a single galaxy, but if we employ the second source redshift estimate from Section 2, $\sim2.6$, we obtain $\sigma\sim315$ km/s, a more common value for massive early-type galaxies. We therefore assume this redshift to infer the predicted time delays, and we obtain $\Delta t_{BC} = 0.1$ days, $\Delta t_{AC} = 1.7$ days and $\Delta t_{DC} = 226.2$ days, with image C leading.

In Figure~\ref{model} we show the critical curve and the caustics, as well as the positions of the source and the observed images. The source is crossing a cusp, which results in the production of three bright images in close proximity, and one isolated faint image. This is a classic configuration for quad lenses. The predicted magnitude differences are shown in Table1~1, and a comparison with the observed values are shown in Figure~\ref{modelphot}.

We find that the predicted brightness ranking of the images is consistent with the observations, with image A being brightest, and image D being faintest. However, there are still large discrepancies between the observed and predicted fluxes. For example, the fluxes of images B and C are different, whereas they are expected to be the same for any smooth mass profile of the lensing galaxy. Such ``flux anomalies'' have been widely encountered for cusp lensed quasars, and can be explained by small-scale structure in the lensing galaxy \citep[e.g.,][]{kee03}. We also remark that the colors of the four images are very similar, which implies that differential extinction is negligible. In any case, differential extinction would not explain the flux discrepancy in image D, as this is $\sim1$ mag \emph{brighter} than expected. Since image D is closest to the lensing galaxy, the stellar density is comparatively high at its location, meaning that microlensing due to stars in the lensing galaxy is a plausible explanation for the discrepancy. Secondly, we remark that the time delays between image D and the other images is large, which means that while intrinsic flux variations between A, B and C will be washed out, they could stand out in image D, and therefore be responsible for the discrepancy. Lastly, small-scale substructure (millilensing) could cause contribute to the discrepancy.

%Firstly light can be affected as it propagates through the main lens galaxy, for example by differential extinction.  This possibility is interesting in light of the color differences between images.  Propagation effects tend to be more important at optical wavelengths than at radio wavelengths; this is particularly true of extinction, although there can be scatter broadening at radio wavelengths. Secondly, the light can be affected by stars in the lens galaxy through microlensing.  This mainly affects optical wavelengths. Finally, the light can be affected by dark matter substructure in the lens galaxy through millilensing.  This could affect all wavelengths.

@@

\begin{itemize}
\item The presence of four point-like images within $\lesssim 3.8\arcsec$ of each other, with similar colors, consistent with quasars templates, but less so with stars and galaxies.
\item The detection of a red galaxy between the point source, such that the relative positions of all five objects are fully consistent with a well-known ``cusp'' configuration. We successfully reproduce this configuration using a SIE + shear model for the lensing galaxy. Further more, the brightness ranking of the point-like images is consistent with the one predicted by the model.
 \item The photometric redshift analysis shows that the galaxy is of elliptical template, typical for lensing galaxies, and of redshift smaller than the point sources. For the inferred redshifts (assuming a source redshift of $\sim2.6$), the velocity dispersion of the lensing galaxy is consistent with those of massive early-type galaxies.
\end{itemize}

@@

\bibitem[Agnello et al.(2015)]{agn15} Agnello A., et al., 2015, MNRAS, 454, 1260 
\bibitem[Arnouts et al.(1999)]{arn99} Arnouts S., Cristiani S., Moscardini L., Matarrese S., Lucchin F., Fontana A., Giallongo E., 1999, MNRAS, 310, 540

\bibitem[Bertin \& Arnouts(1996)]{ber96} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
\bibitem[Bonvin et al.(2017)]{bon17} Bonvin V., et al., 2017, MNRAS, 465, 4914 
\bibitem[Brewer \& Lewis(2008)]{bre08} Brewer, B.~J., \& Lewis, G.~F.\ 2008, \mnras, 390, 39

\bibitem[Chambers et al.(2016)]{cha16} Chambers, K.~C., Magnier, E.~A., Metcalfe, N., et al.\ 2016, arXiv:1612.05560 
\bibitem[Chiba et al.(2005)]{chiba05} Chiba M., Minezaki T., Kashikawa N., Kataza H., Inoue K.~T., 2005, ApJ, 627, 53

\bibitem[Dai et al.(2010)]{dai10} Dai X., Kochanek C.~S., Chartas G., Koz{\l}owski S., Morgan C.~W., Garmire G., Agol E., 2010, ApJ, 709, 278 
\bibitem[Ding et al.(2017)]{din17} Ding X., et al., 2017, preprint (arXiv:1703.02041)

\bibitem[Fadely \& Keeton(2012)]{fad12} Fadely R., Keeton C.~R., 2012, MNRAS, 419, 936 
\bibitem[Finkbeiner et al.(2016)]{fin16} Finkbeiner, D.~P., Schlafly, E.~F., Schlegel, D.~J., et al.\ 2016, \apj, 822, 66

\bibitem[Gaia Collaboration et al.(2016)]{gaia} Gaia Collaboration, Brown, A.~G.~A., Vallenari, A., et al.\ 2016, \aap, 595, A2 
\bibitem[Gelman(1995)]{gel95} Gelman A. et al., 1995, Bayesian Data Analysis. CRC Press, Boca Raton, FL

\bibitem[Ilbert et al.(2006)]{ilb06} Ilbert O., et al., 2006, A\&A, 457, 841

\bibitem[Keeton(2001)]{kee01} Keeton, C.~R.\ 2001, arXiv:astro-ph/0102340 
\bibitem[Keeton, Gaudi, \& Petters(2003)]{kee03} Keeton C.~R., Gaudi B.~S., Petters A.~O., 2003, ApJ, 598, 138 
\bibitem[Kochanek et al.(2000)]{koc00} Kochanek C.~S., et al., 2000, ApJ, 543, 131

\bibitem[McKean et al.(2007)]{mck07} McKean J.~P., et al., 2007, MNRAS, 378, 109 
\bibitem[Moffat (1969)]{mof69} Moffat, A. F. J.\ 1969, \aap, 3, 455
\bibitem[Myers et al.(2003)]{mye03} Myers S.~T., et al., 2003, MNRAS, 341, 1

%% \bibitem[Mateos et al.(2012)]{mat12} Mateos, S., Alonso-Herrero, A., Carrera, F.~J., et al.\ 2012, \mnras, 426, 3271 
\bibitem[Oguri et al.(2006)]{ogu06} Oguri M., et al., 2006, AJ, 132, 999
\bibitem[Oguri \& Marshall(2010)]{ogu10} Oguri, M., \& Marshall, P.~J.\ 2010, \mnras, 405, 2579 
\bibitem[Oguri (2010)]{ogu10b} Oguri M., 2010, PASJ, 62, 1017 
\bibitem[Oguri et al.(2012)]{ogu12} Oguri M., et al., 2012, AJ, 143, 120
\bibitem[Oguri, Rusu, \& Falco(2014)]{ogu14} Oguri M., Rusu C.~E., Falco E.~E., 2014, MNRAS, 439, 2494

@@

\bibitem[Peng et al.(2010)]{peng10} Peng, C.~Y., Ho, L.~C., Impey, C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097 
\bibitem[Reis et al.(2014)]{reis14} Reis, R.~C., Reynolds, M.~T., Miller, J.~M., \& Walton, D.~J.\ 2014, \nat, 507, 207 
\bibitem[Richards et al.(2009)]{ric09} Richards G.~T., et al., 2009, ApJS, 180, 67 
\bibitem[Rusu et al.(2016)]{rus16} Rusu C.~E., et al., 2016, MNRAS, 458, 2

\bibitem[Schlafly \& Finkbeiner(2011)]{sch11} Schlafly, E.~F., \& Finkbeiner, D.~P.\ 2011, \apj, 737, 103 
\bibitem[S{\'e}rsic (1963)]{ser63} S{\'e}rsic J.~L., 1963, BAAA, 6, 41 
\bibitem[Sluse et al.(2003)]{slu03} Sluse, D., Surdej, J., Claeskens, J.-F., et al.\ 2003, \aap, 406, L43 
\bibitem[Sluse et al.(2006)]{slu06} Sluse, D., Claeskens, J.-F., Altieri, B., et al.\ 2006, \aap, 449, 539 
\bibitem[Sluse et al.(2008)]{slu08} Sluse, D., Eigenbrod, A., Courbin, F., et al.\ 2008, Manchester Microlensing Conference, 20 
\bibitem[Sluse et al.(2012)]{slu12} Sluse D., Hutsem{\'e}kers D., Courbin F., Meylan G., Wambsganss J., 2012, A\&A, 544, A62
\bibitem[Sonnenfeld et al.(2017)]{son17} Sonnenfeld A., et al., 2017, arXiv, arXiv:1704.01585

@@

\bibitem[Walsh, Carswell, \& Weymann(1979)]{wal79} Walsh D., Carswell R.~F., Weymann R.~J., 1979, Natur, 279, 381 
\bibitem[Wu \& Jia(2010)]{wu10} Wu, X.-B., \& Jia, Z.\ 2010, \mnras, 406, 1583 
\bibitem[Wu et al.(2012)]{wu12} Wu, X.-B., Hao, G., Jia, Z., Zhang, Y., \& Peng, N.\ 2012, \aj, 144, 49

\bibitem[York et al.(2000)]{york00} York, D.~G., Adelman, J., Anderson, J.~E., Jr., et al.\ 2000, \aj, 120, 1579

@@

\begin{figure}
\epsscale{1}
\plotone{hostlens.eps}
\caption{
Original images ($10\arcsec\times10\arcsec$, first row) and residuals after subtracting the best-fit model with Hostlens. From left to right: $g$, $r$, $i$, $z$, $y$-band. In the second raw, the lensing galaxy is not including in the modeling, whereas in the third raw it is. The images are in linear scale, and cover the full dynamic range. Remaining structure in the residuals amounts to less than 6\% of the peak fluxes and can be attributed to large Poisson noise at the center of the point-like images, as well as to faint arcs expected from the lensed quasar host galaxy, which are not accounted for in the modeling.}
\label{hostlens}
\end{figure}

\begin{figure}
\epsscale{0.6}
\plotone{critcrv1.eps}
\caption{
Gravitational lens modeling. The blue and red lines show the critical curves and caustics, respectively. The green dot shows the quasar position in the source plane, and the black dots show the lens and the observed image positions.}
\label{model}
\end{figure}
